\vspace{-15mm}\fontsize{24pt}{10pt}\selectfont\textbf{\articletitle}

### 2015-04-07 paper/paper.tex

>>>>

\section{Table with computation times}
\begin{tabular}{c|c|c}
Graph & Computation time (without preprocessing) & Computation time (with preprocessing) \\
\hline
cographs1 & 146.8098 sec & 0.0171 sec \\
hugecographs & >30 min & 662.5381 sec \\
cycles175 & 69.8579 & 70.8041 sec \\
bigtrees3 & -1 & -1\\
cubes6 & -1 & -1\\
products72 & -1 & -1\\
torus72 & -1 & -1\\
